Lapse & Vision Loss PS Analysis

### 2025-02-24 analysis.Rmd
fix subclass

  results <- list()
  roundTo <- 2
  for (i in seq_along(formulas)) {
    if(method_name %in% c("cbps", "entropy", "bart")) {
      package <- "WeightIt"
      approach <- "ipw"
    } else if(method_name %in% c("twang_gbm")) {
      package <- "twang"
      approach <- "ipw"
    } else {
      package <- "MatchIt"
      approach <- "match w/ replacement"
    }

    model <- svyglm(formula = formulas[[i]], design = design, family = quasibinomial(), contrasts=NULL)

    model_summary <- summary(model)

    coef_table <- model_summary$coefficients
    estimate <- coef_table[2, "Estimate"]

    roundTo <- 2
    roundP <- 3

    or <- formatC(exp(estimate), format="f", digits=roundTo)
    estimate <- formatC(estimate, format="f", digits=roundTo)
    se <- formatC(coef_table[2, "Std. Error"], format="f", digits=roundTo)
    t_value <- formatC(coef_table[2, "t value"], format="f", digits=roundTo)
    p_value <- formatC(coef_table[2, "Pr(>|t|)"], format="f", digits=roundP)

    confint_values <- confint(model, level = 0.95)[2, ]
    ci_lb <- confint_values[1]
    ci_ub <- confint_values[2]
    ci_lb_or <- formatC(exp(ci_lb), format="f", digits=roundTo)
    ci_ub_or <- formatC(exp(ci_ub), format="f", digits=roundTo)

@@

    rownames(result_summ) <- NULL

    results[[i]] <- result_summ
  }

>>>>

  results <- list()
  roundTo <- 2
  roundP <- 3

  for (i in seq_along(formulas)) {
    if (method_name %in% c("cbps", "entropy", "bart")) {
      package <- "WeightIt"
      approach <- "ipw"
    } else if (method_name %in% c("twang_gbm")) {
      package <- "twang"
      approach <- "ipw"
    } else if (method_name == "subclass") {
      package <- "MatchIt"
      approach <- "subclassification"
    } else {
      package <- "MatchIt"
      approach <- "match w/ replacement"
    }

    if (method_name == "subclass") {
      # Extract subclass weights
      subclass_weights <- weights(design, type = "sampling")

      # Run weighted survey logistic regression
      model <- svyglm(formula = formulas[[i]], design = design, family = quasibinomial(), contrasts = NULL)
    } else {
      # Standard survey logistic regression
      model <- svyglm(formula = formulas[[i]], design = design, family = quasibinomial(), contrasts = NULL)
    }

    model_summary <- summary(model)
    coef_table <- model_summary$coefficients
    estimate <- coef_table[2, "Estimate"]

    or <- formatC(exp(estimate), format = "f", digits = roundTo)
    estimate <- formatC(estimate, format = "f", digits = roundTo)
    se <- formatC(coef_table[2, "Std. Error"], format = "f", digits = roundTo)
    t_value <- formatC(coef_table[2, "t value"], format = "f", digits = roundTo)
    p_value <- formatC(coef_table[2, "Pr(>|t|)"], format = "f", digits = roundP)

    confint_values <- confint(model, level = 0.95)[2, ]
    ci_lb_or <- formatC(exp(confint_values[1]), format = "f", digits = roundTo)
    ci_ub_or <- formatC(exp(confint_values[2]), format = "f", digits = roundTo)

@@

    rownames(result_summ) <- NULL
    results[[i]] <- result_summ
  }
